---
title: "Germplasm descript"
output:
  html_document:
    df_print: paged
---

## Whole germplasm list

If you want to check this germplasm ID that included in the hapmap please see the sorghum germplasm list. This germplasm list includes all germplasm and related information. If you want to genotypic data for subset of the germplasm please submit a list, which including your email address, which kind of data (raw SNP or impuated SNP), to zhenbin@ksu.ed or gpmorris@k-state.edu.

The keyfile used in SNP calling

```{r, echo=FALSE, message=FALSE, warning=FALSE,rows.print=30}
keyfile<-read.csv("~/Desktop/grin/Table_S1.csv",header=T)
DT::datatable(keyfile)
```


##Germplasm distribution

```{r, message=FALSE, warning=FALSE}
library(plotly)
df <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/2014_us_cities.csv')

df$q <- with(df, cut(pop, quantile(pop)))
levels(df$q) <- paste(c("1st", "2nd", "3rd", "4th", "5th"), "Quantile")
df$q <- as.ordered(df$q)

g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showland = TRUE,
  landcolor = toRGB("gray85"),
  subunitwidth = 1,
  countrywidth = 1,
  subunitcolor = toRGB("white"),
  countrycolor = toRGB("white")
)

p <- plot_geo(df, locationmode = 'USA-states', sizes = c(1, 250)) %>%
  add_markers(
    x = ~lon, y = ~lat, size = ~pop, color = ~q, hoverinfo = "text",
    text = ~paste(df$name, "<br />", df$pop/1e6, " million")
  ) %>%
  layout(title = '2014 US city populations<br>(Click legend to toggle)', geo = g)
p
```



If you need GBS data, please pick out the germplasm ID from the Sorghum Germplasm list. Then submit it to: zhenbin@ksu.edu or gpmorris@ksu.edu. Then they will send you a link to download the genomic data and the links will be remove after 7 days of the email send.


If you use data from this dataset, please cite:


If you use data from this dataset for specific population, please included the original paper in your reference list.


We thanks all of people who generated data. It's a really hard and time comsuming proccesses. So we preciate those who share their data. We hope we can contribute a little our energy by intergate those data together to make a public dataset for all sorghum genomic research.

This SNP dataset will be updated after we recieve new data.

References: